Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes

### 2025-05-03 code/analysis-code/Statistical_Analysis.qmd
Final Update

# 6) Print the final table
print(result_table)

@@

```{r calibration-plot, fig.width=6, fig.height=6, warning=FALSE}
# assume `cal` is your calibrate() object from rms::calibrate(lrm_fit, method="boot", B=200)

# 1) Plot without default legend
plot(cal,
     lty    = c(3, 1, 2),                             # dashed, solid, dashed
     col    = c("#1f78b4", "#33a02c", "#e31a1c"),     # blue, green, red
     lwd    = 2,
     xlab   = "Predicted Probability of Adverse Outcome",
     ylab   = "Observed Proportion of Adverse Outcome",
     main   = "Calibration of Gravidity Model\nin Women Aged < 25",
     legend = FALSE,                                  # <-- turn off built‐in legend
     xlim   = c(0.4, 0.8),
     ylim   = c(0.4, 0.8)
)

@@

```{r}
# only these variables are needed for the logistic model
dd <- datadist(
  train_data[, c(
    "gravidity",
    "total_malaria_episodes",
    "study_arm",
    "education_level",
    "adverse_birth_outcome"
  )]
)
options(datadist = "dd")

>>>>

# 6) Print the final table
print(result_table)
```

@@

```{r calibration-plot, fig.width=6, fig.height=6, warning=FALSE}
# 1) Plot without default legend
plot(cal,
     lty    = c(3, 1, 2),                             # dashed, solid, dashed
     col    = c("#1f78b4", "#33a02c", "#e31a1c"),     # blue, green, red
     lwd    = 2,
     xlab   = "Predicted Probability of Adverse Outcome",
     ylab   = "Observed Proportion of Adverse Outcome",
     main   = "Calibration of Gravidity Model\nin Women Aged < 25",
     legend = FALSE,                                  # <-- turn off built‐in legend
     xlim   = c(0.4, 0.8),
     ylim   = c(0.4, 0.8)
)

@@

```{r}
dd <- datadist(
  train_data[, c(
    "gravidity",
    "total_malaria_episodes",
    "study_arm",
    "education_level",
    "adverse_birth_outcome"
  )]
)
options(datadist = "dd")

### 2025-05-03 products/manuscript/supplement/Supplementary-Material.qmd
Final Update

Explain here what each code/file is and does, and in which order (if any) users need to run thing to reproduce everything.
Essentially, give a full set of instructions to re-generate everything.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
library(here)
here::i_am("products/manuscript/Manuscript.qmd")

# ← THIS is the one that actually sets the working dir for *all* chunks:
library(knitr)
knitr::opts_chunk$set(root.dir = here::here("products/manuscript"))

@@

# Additional Method Details

Often, the main manuscript only allows for an overview description of the methods. Use the supplement to describe all your methods, models and approaches in a lot of detail. Reference specific parts of your code as needed.

@@

Show additional results here. Those can be some useful exploratory/descriptive figures or tables, or results from additional analyses that didn't make it into the main text.

*Bar Graph of Total Malaria Episodes During Pregnancy by Treatment Arm*

@@

*Bar Graphs for Gravidity and Parity*

@@

*Parity Distribution by Treatment Arm*

@@

## Example additional result

@tbl-resulttable1 shows an additional table summarizing a model fit.

@@

@fig-result2 shows a scatterplot figure produced by one of the R scripts.

#  Evaluating Discrimination (ROC Curve and AUC)

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# 1) Load required libraries
library(dplyr)
library(pROC)
library(caret)
library(here)

@@

I see that the ROC curve for my model is close to the diagonal, with an AUC only slightly above 0.5. This tells me that the model doesn't have strong discriminative ability for predicting adverse outcomes in women under 25. Additionally, the calibration plot shows that my predicted probabilities often stray from the ideal diagonal—especially in the mid-range—indicating that my model’s risk estimates don't consistently match the observed rates. Overall, while gravidity is statistically significant, my model as a whole isn't very effective at distinguishing between those who experience adverse outcomes and those who don't, and its probability estimates need improvement.

@@

# Discussion

# References

>>>>

@@

&nbsp;
&nbsp;

The Supplementary Appendix is built with a clear, step‑wise workflow: raw PROMO trial data are first cleaned and documented, then transformed into the analysis dataset. Subsequent scripts generate missingness tables, interaction model diagnostics, machine‑learning tuning results, and additional stratified analyses. Each RMarkdown file lives in the code/ subfolders (processing, EDA, analysis), reads from data/, and writes results into results/. Finally, the Quarto source in products/manuscript/supplement renders the assembled tables and figures into Supplementary‑Material.docx. Running the scripts in their numeric order fully reproduces every table and figure in this appendix.

## 📁 Directory Structure Overview
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# From products/manuscript/supplement → go up to products/manuscript, then into Images/
knitr::include_graphics("../Images/Project-root.png")
```

@@

# # Exploratory Analysis: Malaria Episodes, Gravidity/Parity, and Treatment Arm

The four supplementary EDA plots concisely overview key baseline characteristics by treatment arm and the height–weight relationship at enrollment. The first panel shows that the majority of women experienced one malaria episode during pregnancy, with progressively fewer in the 2–3 and ≥4 categories and that counts are consistently higher in the DP arm than the SP arm across all episode bins. The second panel depicts gravidity stratified into 1, 2–3, and ≥4 pregnancies, revealing a similar pattern in both arms but a noticeably smaller proportion of primigravidae in the SP group. The third panel presents parity categories (0, 1–2, ≥3), again demonstrating broadly comparable distributions between arms, with a slight excess of women with ≥3 previous births in the DP arm. Finally, the scatterplot of maternal height and weight, with a LOESS smoothing curve and 95% confidence band, confirms a modest positive association between height and weight at enrollment, supporting the use of both measures in downstream modeling.

*Figure S1.Total Malaria Episodes During Pregnancy by Treatment Arm*
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(here)

@@

&nbsp;
&nbsp;

*Figure S2: Gravidity Distribution by Treatment Arm*

@@

&nbsp;
&nbsp;

*Figure S3: Parity Distribution by Treatment Arm*

@@

&nbsp;
&nbsp;

*Figure S4:Scatterplot of maternal weight by height with fitted LOESS smoothing curve (95% CI) — exploratory assessment of the height–weight relationship at enrollment*

&nbsp;
&nbsp;

## Additional result

*Table 1: Regression Coefficients for the Association Between Weight and Outcome*

@@

&nbsp;
&nbsp;

#  Evaluating Discrimination (ROC Curve and AUC)
*Additional Model Evaluation (Supplement)*
 Panel A shows the ROC curve for the gravidity‐only logistic model in women under 25. The curve lies modestly above the diagonal, reflecting fair discrimination (AUC ≈ 0.55).
 Panel B is the corresponding calibration plot (decile‐based), which compares observed event rates within probability bins to the ideal 45° line; slight deviations indicate some miscalibration in the highest and lowest risk groups.

 Panel C presents the bootstrap bias‐corrected calibration curve (200 resamples). The “apparent” (dotted) and “bias‐corrected” (solid) lines both track closely to the ideal (dashed) reference, confirming good overall calibration (mean absolute error ≈ 0.016).
 Panel D displays the heatmap of cross‐validated AUC across the elastic‐net penalty–mixture grid, illustrating that intermediate penalty values (log₁₀λ around –2) and mixture α near 0.8 yielded the best discrimination.

 Finally, Table S7 reports the mean (±SE) cross‐validated ROC AUC for the three machine‐learning algorithms: LASSO (0.55±0.012), random forest (0.52±0.013), and XGBoost (0.497±0.014). This confirms that regularized regression slightly outperformed the tree‐based methods under our tuning scheme.

*Supplementary Regression Coefficients (Table S8)*
 The simple linear model of weight on height yields an intercept of 149.7g (SE 19.8, p<0.001) and a non‐significant slope of 0.23g/cm (SE 0.27, p=0.43), indicating that while taller women tended to weigh more on average, this association was weak and did not reach statistical significance in our sample.

 &nbsp;
&nbsp;

*Figure S5: Calibration Plot: Gravidity Model (Age < 25)*
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# 1) Load required libraries
library(dplyr)
library(pROC)
library(caret)
library(here)

@@

&nbsp;
&nbsp;

**Figure S6. Bootstrap‑calibrated calibration curve for the malaria interaction model**
```{r, echo=FALSE, message=FALSE, warning=FALSE}

knitr::include_graphics("../Images/rms_model.png")

```
&nbsp;
&nbsp;

*Figure S7: Calibration curve for malaria interaction model in women aged <25 years*

```{r, echo=FALSE, message=FALSE, warning=FALSE}

knitr::include_graphics("../Images/CalibrationPlot.png")

```
&nbsp;
&nbsp;

*Figure S8:Heatmap of five‑fold cross‑validated ROC AUC across the elastic‑net penalty–mixture grid*
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("../Images/Heatmap.CV AUC.png")

&nbsp;
&nbsp;

*Table S2:Mean cross‑validated ROC AUC (±SE) for each machine‑learning mode*
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("../Images/MeanCV ROC.AUC .png")

@@

# Discussion
The supplementary materials deepen and validate our primary findings by providing transparent documentation of all data‐processing steps, extensive methodological details, and additional model diagnostics that could not be accommodated in the main text. Detailed tables of missingness, deviance tests, and variance inflation factors reinforce the robustness of our interaction model. At the same time, the bootstrap and decile‐based calibration curves confirm its reliability across risk strata. The elastic‐net heatmap and cross‐validated AUC summaries for LASSO, random forest, and XGBoost highlight that, under consistent tuning, regularized regression offers the strongest discrimination in our dataset. Exploratory bar charts of malaria episodes, gravidity, and parity by treatment arm contextualize cohort characteristics, and the gravidity‐only subgroup analyses (ROC and calibration plots) elucidate how prior pregnancy history predicts adverse outcomes among younger women. Together, these supplementary analyses enhance confidence in our conclusions, demonstrate reproducibility, and offer a resource for readers seeking to replicate or extend this work.

### 2025-05-03 products/manuscript/supplement/Supplementary-Material.tex
Final Update

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.33,0.33}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.42,0.45,0.49}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.84,0.23,0.29}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.36,0.77}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.84,0.23,0.29}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.01,0.18,0.38}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.42,0.45,0.49}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.42,0.45,0.49}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.36,0.77}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.84,0.23,0.29}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.84,0.23,0.29}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.36,0.77}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.42,0.45,0.49}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.33,0.33}{\underline{#1}}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.84,0.23,0.29}{\textbf{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.36,0.77}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.44,0.26,0.76}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.01,0.18,0.38}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.42,0.45,0.49}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.84,0.23,0.29}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.14,0.16,0.18}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.14,0.16,0.18}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.44,0.26,0.76}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.84,0.23,0.29}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.42,0.45,0.49}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.36,0.77}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.01,0.18,0.38}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.01,0.18,0.38}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.89,0.38,0.04}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.01,0.18,0.38}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{1.00,0.33,0.33}{#1}}

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary Materials of Impact of IPTp Regimen on Pregnancy
Outcomes}
\author{}
\date{}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load necessary libraries}
\FunctionTok{library}\NormalTok{(dplyr)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(here)}

\CommentTok{\# Read in the cleaned data}
\NormalTok{promo\_data\_clean }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"clean"}\NormalTok{, }\StringTok{"PROMO\_Data\_clean.csv"}\NormalTok{))}

\CommentTok{\# Recode \textquotesingle{}total\_malaria\_episodes\_during\_pregnancy\textquotesingle{} into a categorical variable}
\NormalTok{promo\_data\_clean }\OtherTok{\textless{}{-}}\NormalTok{ promo\_data\_clean }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{MalariaEpisodesPreg\_cat =} \FunctionTok{case\_when}\NormalTok{(}
\NormalTok{      total\_malaria\_episodes\_during\_pregnancy }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"1"}\NormalTok{,}
\NormalTok{      total\_malaria\_episodes\_during\_pregnancy }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{, }\DecValTok{3}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"2–3"}\NormalTok{,}
\NormalTok{      total\_malaria\_episodes\_during\_pregnancy }\SpecialCharTok{\textgreater{}=} \DecValTok{4} \SpecialCharTok{\textasciitilde{}} \StringTok{"≥4"}
\NormalTok{    ),}
    \AttributeTok{MalariaEpisodesPreg\_cat =} \FunctionTok{factor}\NormalTok{(MalariaEpisodesPreg\_cat, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2–3"}\NormalTok{, }\StringTok{"≥4"}\NormalTok{))}
\NormalTok{  )}

\CommentTok{\# Create the bar graph}
\FunctionTok{ggplot}\NormalTok{(promo\_data\_clean, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ MalariaEpisodesPreg\_cat, }\AttributeTok{fill =}\NormalTok{ study\_arm)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{"dodge"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Total Malaria Episodes During Pregnancy by Treatment Arm"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Total Malaria Episodes During Pregnancy (Categorical)"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{fill =} \StringTok{"Treatment Arm"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load necessary libraries}

\CommentTok{\# Read in the cleaned data}
\NormalTok{promo\_data\_clean }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"clean"}\NormalTok{, }\StringTok{"PROMO\_Data\_clean.csv"}\NormalTok{))}

\CommentTok{\# Recode Gravidity into categories: "1", "2–3", "≥4"}
\NormalTok{promo\_data\_clean }\OtherTok{\textless{}{-}}\NormalTok{ promo\_data\_clean }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{Gravidity\_cat =} \FunctionTok{case\_when}\NormalTok{(}
\NormalTok{      gravidity }\SpecialCharTok{==} \DecValTok{1} \SpecialCharTok{\textasciitilde{}} \StringTok{"1"}\NormalTok{,}
\NormalTok{      gravidity }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{, }\DecValTok{3}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"2–3"}\NormalTok{,}
\NormalTok{      gravidity }\SpecialCharTok{\textgreater{}=} \DecValTok{4} \SpecialCharTok{\textasciitilde{}} \StringTok{"≥4"}
\NormalTok{    ),}
    \AttributeTok{Gravidity\_cat =} \FunctionTok{factor}\NormalTok{(Gravidity\_cat, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"1"}\NormalTok{, }\StringTok{"2–3"}\NormalTok{, }\StringTok{"≥4"}\NormalTok{))}
\NormalTok{  )}

\CommentTok{\# Create the bar graph for Gravidity by Treatment Arm}
\FunctionTok{ggplot}\NormalTok{(promo\_data\_clean, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Gravidity\_cat, }\AttributeTok{fill =}\NormalTok{ study\_arm)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{"dodge"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Gravidity Distribution by Treatment Arm"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Gravidity Category (1, 2–3, ≥4)"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{fill =} \StringTok{"Treatment Arm"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Load necessary libraries}
\FunctionTok{library}\NormalTok{(dplyr)}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{library}\NormalTok{(here)}

\CommentTok{\# Read in the cleaned data}
\NormalTok{promo\_data\_clean }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"clean"}\NormalTok{, }\StringTok{"PROMO\_Data\_clean.csv"}\NormalTok{))}

\CommentTok{\# Recode Parity into categories: "0", "1–2", "≥3"}
\NormalTok{promo\_data\_clean }\OtherTok{\textless{}{-}}\NormalTok{ promo\_data\_clean }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \AttributeTok{Parity\_cat =} \FunctionTok{case\_when}\NormalTok{(}
\NormalTok{      parity }\SpecialCharTok{==} \DecValTok{0} \SpecialCharTok{\textasciitilde{}} \StringTok{"0"}\NormalTok{,}
\NormalTok{      parity }\SpecialCharTok{\%in\%} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{) }\SpecialCharTok{\textasciitilde{}} \StringTok{"1–2"}\NormalTok{,}
\NormalTok{      parity }\SpecialCharTok{\textgreater{}=} \DecValTok{3} \SpecialCharTok{\textasciitilde{}} \StringTok{"≥3"}
\NormalTok{    ),}
    \AttributeTok{Parity\_cat =} \FunctionTok{factor}\NormalTok{(Parity\_cat, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\StringTok{"0"}\NormalTok{, }\StringTok{"1–2"}\NormalTok{, }\StringTok{"≥3"}\NormalTok{))}
\NormalTok{  )}

\CommentTok{\# Create the bar graph for Parity by Treatment Arm}
\FunctionTok{ggplot}\NormalTok{(promo\_data\_clean, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Parity\_cat, }\AttributeTok{fill =}\NormalTok{ study\_arm)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{position =} \StringTok{"dodge"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Parity Distribution by Treatment Arm"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Parity Category (0, 1–2, ≥3)"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{fill =} \StringTok{"Treatment Arm"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# 1) Load required libraries}
\FunctionTok{library}\NormalTok{(dplyr)}
\FunctionTok{library}\NormalTok{(pROC)}
\FunctionTok{library}\NormalTok{(caret)}
\FunctionTok{library}\NormalTok{(here)}

\CommentTok{\# 2) Read cleaned data and subset to women \textless{} 25}
\NormalTok{promo\_data\_clean }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"data/clean/PROMO\_Data\_clean.csv"}\NormalTok{))}
\NormalTok{promo\_data\_young }\OtherTok{\textless{}{-}}\NormalTok{ promo\_data\_clean }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(age\_at\_enrollment\_years }\SpecialCharTok{\textless{}} \DecValTok{25}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}
    \CommentTok{\# Composite adverse outcome: 1 if preterm, stillbirth, or low birth weight}
    \AttributeTok{low\_birth\_weight      =} \FunctionTok{as.integer}\NormalTok{(birth\_weight }\SpecialCharTok{\textless{}} \FloatTok{2.5}\NormalTok{),}
    \AttributeTok{adverse\_birth\_outcome =} \FunctionTok{as.integer}\NormalTok{(}
\NormalTok{      preterm\_births\_count }\SpecialCharTok{\textgreater{}} \DecValTok{0} \SpecialCharTok{|}
\NormalTok{      stillbirth\_bin }\SpecialCharTok{==} \DecValTok{1}        \SpecialCharTok{|}
\NormalTok{      low\_birth\_weight }\SpecialCharTok{==} \DecValTok{1}
\NormalTok{    )}
\NormalTok{  )}

\CommentTok{\# 3) Fit logistic regression model}
\NormalTok{model\_gravidity }\OtherTok{\textless{}{-}} \FunctionTok{glm}\NormalTok{(}
\NormalTok{  adverse\_birth\_outcome }\SpecialCharTok{\textasciitilde{}}\NormalTok{ gravidity }\SpecialCharTok{+}\NormalTok{ total\_malaria\_episodes }\SpecialCharTok{+}
\NormalTok{    study\_arm }\SpecialCharTok{+}\NormalTok{ education\_level,}
  \AttributeTok{family =} \FunctionTok{binomial}\NormalTok{(}\AttributeTok{link =} \StringTok{"logit"}\NormalTok{),}
  \AttributeTok{data   =}\NormalTok{ promo\_data\_young}
\NormalTok{)}

\CommentTok{\# 4) Generate predicted probabilities}
\NormalTok{promo\_data\_young}\SpecialCharTok{$}\NormalTok{predicted\_prob }\OtherTok{\textless{}{-}} \FunctionTok{predict}\NormalTok{(}
\NormalTok{  model\_gravidity,}
  \AttributeTok{newdata =}\NormalTok{ promo\_data\_young,}
  \AttributeTok{type    =} \StringTok{"response"}
\NormalTok{)}

\CommentTok{\# 5) ROC curve and AUC}
\NormalTok{roc\_obj  }\OtherTok{\textless{}{-}} \FunctionTok{roc}\NormalTok{(}
\NormalTok{  promo\_data\_young}\SpecialCharTok{$}\NormalTok{adverse\_birth\_outcome,}
\NormalTok{  promo\_data\_young}\SpecialCharTok{$}\NormalTok{predicted\_prob}
\NormalTok{)}
\FunctionTok{plot}\NormalTok{(}
\NormalTok{  roc\_obj,}
  \AttributeTok{col   =} \StringTok{"blue"}\NormalTok{,}
  \AttributeTok{lwd   =} \DecValTok{2}\NormalTok{,}
  \AttributeTok{main  =} \StringTok{"ROC Curve: Gravidity Model (Age \textless{} 25)"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\pandocbounded{\includegraphics[keepaspectratio]{Supplementary-Material_files/figure-pdf/roc-calibration-1.pdf}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{auc\_val }\OtherTok{\textless{}{-}} \FunctionTok{auc}\NormalTok{(roc\_obj)}
\FunctionTok{cat}\NormalTok{(}\StringTok{"AUC:"}\NormalTok{, }\FunctionTok{round}\NormalTok{(auc\_val, }\DecValTok{2}\NormalTok{), }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# 6) Calibration plot}
\NormalTok{data\_cal }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}
  \AttributeTok{observed =} \FunctionTok{factor}\NormalTok{(promo\_data\_young}\SpecialCharTok{$}\NormalTok{adverse\_birth\_outcome, }\AttributeTok{levels =} \FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\DecValTok{1}\NormalTok{)),}
  \AttributeTok{predicted =}\NormalTok{ promo\_data\_young}\SpecialCharTok{$}\NormalTok{predicted\_prob}
\NormalTok{)}
\NormalTok{cal\_plot }\OtherTok{\textless{}{-}} \FunctionTok{calibration}\NormalTok{(}
\NormalTok{  observed }\SpecialCharTok{\textasciitilde{}}\NormalTok{ predicted,}
  \AttributeTok{data  =}\NormalTok{ data\_cal,}
  \AttributeTok{class =} \StringTok{"1"}
\NormalTok{)}
\FunctionTok{plot}\NormalTok{(cal\_plot, }\AttributeTok{main =} \StringTok{"Calibration Plot: Gravidity Model (Age \textless{} 25)"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\pandocbounded{\includegraphics[keepaspectratio]{Supplementary-Material_files/figure-pdf/roc-calibration-2.pdf}}

>>>>

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary Materials of Impact of IPTp Regimen on Pregnancy Outcomes},
  pdfauthor={Asmith Joseph},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary Materials of Impact of IPTp Regimen on Pregnancy
Outcomes}
\author{Asmith Joseph}
\date{}

@@

@@

@@

@@

@@

\pandocbounded{\includegraphics[keepaspectratio]{Supplementary-Material_files/figure-pdf/unnamed-chunk-9-1.pdf}}

\pandocbounded{\includegraphics[keepaspectratio]{Supplementary-Material_files/figure-pdf/unnamed-chunk-9-2.pdf}}
